Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-01-22 AO_bondedSi.tex
document compiles with GP section and long equations, added the IR image pdf
Add the derived Gap Sizes table

We looked for the indication of large gaps detectable as ``IR bubbles'' \cite{1992JEMat..21..669M} with IR imaging.  The detector was an IR Vista $\alpha$NIR infrared focal plane array, with 312 $\times$ 252 pixels, with 30 $\mu$m square pixels.  We used a 50 mm F/2 lens, with a fiber optic white light illumination source.  The combination of the absorption of Si, the lamp spectrum and the detector responsivity led to an effective bandpass from approximately 1.15$-$1.6 $\mu$m.  The field of view was smaller than the 100 mm diameter wafers, so we dithered the sample.  No effort was made to flat field the detector, so copious detector non-uniformities and vignetting are present in our images.  It was easy to detect IR bubbles despite the detector artifacts since the bubbles translate with the sample when we dither its position.  We detected IR bubbles in all 3 of the bonded Si samples on which we recorded IR images.  The bubble areal density varied from about 4 per 100 mm diameter bonded wafer pair to over 20 per bonded wafer pair.  As expected, the unbonded DSP wafers show no such IR bubbles.  No attempt at quantitative measurement was made on the IR images due to evidence that the detector is non-linear.  The morphology was clear regardless of the detector response.

@@

\section{Results of infrared spectroscopy of directly bonded Si}
\label{secResults}
In this section we describe the spectroscopy of directly bonded Si.  In some instances IR imaging was available and was leveraged to target or avoid locations demonstrating IR bubbles.  In other cases the IR imaging was not available or ignored, and spectra were taken at random positions on the wafer surface.

@@

We set our priors \verb|\cite{someStatisticsBook}| on $\ln{a}$, $\ln{s}$, $d$, and $f$ as uniform over a wide range of values consistent with visual inspection of each spectrum.  The final un-normalized posterior probability function, expressed as a natural logarithm is:

\begin{equation}
	\ln{p(d,f,a,s|\lambda, T_{obs}, \sigma)} \propto \ln{p(d,f,a,s)} -0.5\;\boldsymbol{r^\intercal}\boldsymbol{C^{-1}}\boldsymbol{r}} -0.5 \ln{\det{\boldsymbol{C}}} \label{eqnPosterior}
\end{equation}

where the residual vector $\boldsymbol{r}$ is the data $T_{obs}$ minus the model $T_{mix}$.  We produce posterior samples with Markov Chain Monte Carlo (MCMC).  Specifically, we implemented \texttt{emcee}\footnote{https://github.com/dfm/emcee}\cite{emcee}, with 32 walkers, hundreds of burn-in samples, and 600-1000 iterations.  We initialized the walkers in the vicinity of our best guess for parameters based on visual inspection of the observed normalized Transmission spectra.  Figures \ref{figVG03full, figVG03part, figVG12_corner} show examples of posterior samples including corner plots of the interesting physical parameters $d$ and $f$.

\subsection{Spectra of direct bonded Si with known gap sizes}
\label{secKnownGaps}
Figures \ref{figVG03full} to \ref{figVG12_f50} show examples of the predicted and measured IR spectra.  Figure \ref{figVG03_f100} shows an example spectrum in which the measurement is consistent with the prediction for a gap with the known conditions.  Meanwhile, Figure \ref{figVG12_f50} shows a spectrum in which the measurement marginally exceeds the prediction (by about $\sim 3 \sigma$).  Other parts show less consistency with the prediction due to the difficulty of direct-bonding Si in the absence of thermal annealing.

@@

A key result of this work is to show that gaps of known dimensions are recovered in our spectroscopy.  The cases in which predicted spectroscopy differs from measurement are due to either a bona-fide detection of a gap above and beyond the implanted gap, or some measurement artifacts.  In the next section we address mitigation of artifacts.

\subsection{Mitigation of measurement artifacts}
We mitigated measurement artifacts in the following ways.  We have mostly been able to rule out wavelength-dependent diffraction from the mesh pattern as a measurement artifact, since the beam size is large and the angular spread of diffraction from the mesh pattern would be much smaller than the spread of the beam.  Still, to remove this concern, we moved to using the coarse mesh rather than the medium or fine meshes, when possible.  We saw no difference in the bond quality surrounding the medium or fine meshes, which is consistent with results from the literature \cite{1992JEMat..21..669M}.  Specifically, the gas pressure of bonded wafers grows as the fill factor of gaps decreased.  In other words, what matters is the fill factor of gaps, not their relative sizes.  Since the fine, medium, and coarse meshes had the same fill factors, we anticipate no difference in the pressure of the gaps, and therefore no difference in the bonding properties.

\subsection{Spectra of direct bonded Si with no intentionally implanted gap}
We have shown that the IR spectroscopy technique combined with the Fabry-P\'{e}rot framework provide accurate knowledge of the gap size.  In the cases where we expected no gap (i.e. perfect Si-Si bond), we have seen spectra consistent with 100\% transmission relative to a DSP Si wafer.  In other cases we have seen evidence for gaps, which is simply an indication that the bonding process introduces gaps.

>>>>

We looked for the indication of large gaps detectable as ``IR bubbles'' \cite{1992JEMat..21..669M} with IR imaging.  The detector was an IR Vista $\alpha$NIR infrared focal plane array, with 312 $\times$ 252 pixels, with 30 $\mu$m square pixels.  We used a 50 mm F/2 lens, with a fiber optic white light illumination source.  The combination of the absorption of Si, the lamp spectrum and the detector responsivity led to an effective bandpass from approximately 1.15$-$1.6 $\mu$m.  The field of view was smaller than the 100 mm diameter wafers, so we dithered the sample.  Figure \ref{figVS2021_IR_image} shows an IR image of sample VS20-21.  For this image we coarsely flat fielded the detector by observing a homogeneously illuminated white screen. Despite the flat fielding, detector non-uniformities and vignetting are perceptible in our image as vertical stripes.  Mosaic-stitching errors are also perceptible.  It was easy to detect IR bubbles despite detector artifacts since the bubbles translate with the sample when we dither its position.  We detected IR bubbles in all 3 of the bonded Si samples on which we recorded IR images.  The bubble areal density varied from about 4 per 100 mm diameter bonded wafer pair to over 20 per bonded wafer pair.  The individual IR bubble diameters were as small as a few square millimeters up to 400 mm$^2$.  The morphologies of the IR bubbles ranged from perfectly circular to irregular.  The structure within the IR bubbles was sometimes indicative of Newton's rings, exposing the presence of gaps larger than about $\lambda/2$ up to $\sim 15 \lambda$.  As expected, the unbonded DSP wafers show no such IR bubbles.  No attempt at quantitative measurement was made on the IR images due to evidence of a non-linear detector response.  The bulk morphologies were clear regardless of the detector response.  When IR imaging was available, it was leveraged to target IR specectrscopy in locations demonstrating presence or absense of IR bubbles, as desired.  In other cases when IR imaging was not available or ignored, spectra were taken at random positions on the wafer.

@@

\section{Results of infrared spectroscopy of directly bonded Si}
\label{secResults}
In this section we describe the spectroscopy of directly bonded Si.

@@

We set our prior probability distribution functions \verb|\cite{someStatisticsBook}|, $\ln{p(d,f,a,s)}$ as uniform over a wide range of values for $\ln{a}$, $\ln{s}$, $d$, and $f$ consistent with visual inspection of each spectrum.  The final un-normalized posterior probability function, expressed as a natural logarithm is:

\begin{equation}
	\ln{p(d,f,a,s|\lambda, T_{obs}, \sigma)} \propto \ln{p(d,f,a,s)} -0.5\;\boldsymbol{r^\intercal}\boldsymbol{C^{-1}}\boldsymbol{r} -0.5\;\ln{\det{\boldsymbol{C}}} \label{eqnPosterior}
\end{equation}

where the residual vector $\boldsymbol{r}$ is the data $T_{obs}$ minus the model $T_{mix}$.  We produce posterior samples with Markov Chain Monte Carlo (MCMC).  Specifically, we implemented \texttt{emcee}\footnote{https://github.com/dfm/emcee}\cite{emcee}, with 32 walkers, hundreds of burn-in samples, and 600-1000 iterations.  We initialized the walkers in the vicinity of our best guess for parameters based on visual inspection of the observed normalized Transmission spectra.  Figures \ref{figVG03full}, \ref{figVG03part}, and \ref{figVG12_corner} show examples of posterior samples including corner plots of the interesting physical parameters $d$ and $f$.

\subsection{Spectra of direct bonded Si with known gap sizes}
\label{secKnownGaps}
Figures \ref{figVG03full} to \ref{figVG12} show examples of the predicted and measured IR spectra.  Figure \ref{figVG03_f100} shows an example spectrum in which the measurement is consistent with the prediction for a gap with the known conditions.  Meanwhile, Figure \ref{figVG12_f50} shows a spectrum in which the measurement marginally exceeds the prediction (by about $\sim 3 \sigma$).  Other parts show less consistency with the prediction due to the difficulty of direct-bonding Si in the absence of thermal annealing.

@@

A key result of this work is to show that gaps of known dimensions are recovered in our spectroscopy.  Table \verb|\ref{tbl_DerivedGapSizes}| summarizes the outcome of some measurements in the areas with known gaps and fill factors.  The table lists the median sample and 68\% confidence intervals.

\subsection{TODO: Comparison of Transmission-spectroscopy derived gap sizes with lab-measured gap size}
\subsection{TODO: Spectra of direct bonded Si with no intentionally implanted gaps}
\section{TODO: Discussion}

\subsection{TODO: Mitigation of measurement artifacts}
We mitigated measurement artifacts in the following ways.  We have mostly been able to rule out wavelength-dependent diffraction from the mesh pattern as a measurement artifact, since the beam size is large and the angular spread of diffraction from the mesh pattern would be much smaller than the spread of the beam.  Still, to remove this concern, we moved to using the coarse mesh rather than the medium or fine meshes, when possible.  We saw no difference in the bond quality surrounding the medium or fine meshes, which is consistent with results from the literature \cite{1992JEMat..21..669M}.  Specifically, the gas pressure of bonded wafers grows as the fill factor of gaps decreased.  In other words, what matters is the fill factor of gaps, not their relative sizes.  Since the fine, medium, and coarse meshes had the same fill factors, we anticipate no difference in the pressure of the gaps, and therefore no difference in the bonding properties.
